A Survey of Scientific Workflow Management Systems

### 2014-05-06 paper.tex
update citations

\begin{enumerate}
\item \textbf{Bulk Work.}
Workflows are often used to perform computational work in bulk. This could be
bulk data processing or running multiple distinct processing tasks on a single
set of data. In addition to carrying out such work, workflow environments
provide oppurtunities for giving structure and order to a set of tasks and
often with sufficient expressivity, choices and selections to carry out a bulk
of work selectively. Some of the examples of such work are \emph{parameter
sweeps} where tasks are run over a series of parameter values, \emph{ensemble
studies} where tasks are carried out over discrete groups of parameters over a
space.

@@

\paragraph{Dataflow and Functional Languages} Functional and Dataflow languages
and their derivatives have been a viable choice for workflow languages
paradigm. In the dataflow paradigm, a workflow processor will `fire' when the
data sufficient for its firing is available. Dataflow programming paradigm
particularly suites the workflow approach of programming. There are many
research works advocating a dataflow oriented approach to solve problems
involving a flow of data among computing components, predominantly in a
Directed Acyclic Graph form \cite{dataflow,lee-messerschmitt:1987}. Early
research on dataflow languages as visual language \cite{sutherland:1966}
reinforce the notion of the suitability of dataflow paradigm for workflows.

>>>>

\begin{enumerate}
\item \textbf{Bulk Work.}
Workflows are important because they enable to perform computational work in
bulk. This could be bulk data processing or running multiple distinct
processing tasks on a single set of data. In addition to carrying out such
work, workflow environments provide oppurtunities for giving structure and
order to a set of tasks and often with sufficient expressivity, choices and
selections to carry out a bulk of work selectively. Some of the examples of
such work are \emph{parameter sweeps} where tasks are run over a series of
parameter values, \emph{ensemble studies} where tasks are carried out over
discrete groups of parameters over a space.

@@

\paragraph{Dataflow and Functional Languages} Functional and Dataflow languages
and their derivatives have been a viable choice for workflow languages
paradigm. In the dataflow paradigm, a workflow processor will `fire' when the
data sufficient for its firing is available. Dataflow programming paradigm
particularly suites the workflow approach of programming. There are many
research works advocating a dataflow oriented approach to solve problems
involving a flow of data among computing components, predominantly in a
Directed Acyclic Graph form \cite{dataflow,lee-messerschmitt:1987}. Early
research on dataflow languages as visual language~\cite{sutherland:1966}
reinforce the notion of the suitability of dataflow paradigm for workflows.
